\centering DAOSYS: Smart DAO Protocol for Decentralized Finance

### 2022-09-27 latex/whitepaper/article.tex
final draft

\documentclass[journal,twocolumn,12pt]{ieeesyscoin}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{lipsum}
\usepackage{makecell}
\usepackage[switch]{lineno}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\linenumbers
\history{}

@@

\begin{abstract}
Despite popular perception, treasuries of Dentralized Autonomous Organizations (DAOs) tend to be centrally controlled and do not reflect the true ethos of cryptocurrency (i.e., \textit{not your keys, not your coins}). DAOSYS solves this problem with its new Autonomous Service Engine (ASE) technology by deploying a reference platform for self-sovereign capital coordination. Through the ASE, the DAOSYS token will serve as a protocol layer creating a fully backed non-speculative asset allowing for quick seamless deployment of child DAOs in a secure manner. This is made possible by innovating on the multi-faceted proxy standard defined in EIP-2535. The ASE will serve as the cornerstone of all SYS Labs decentralized finance (DeFi) products, as supported by the Syscoin Platform.
\end{abstract}

@@

The objective of a decentralized autonomous organization (DAO) is to solve the principal-agent dilemma. This dilemma is a result of misaligned incentives where agents acting in a system are incentivized towards their own benefit over the benefit of a principle or other agents acting within the system \cite{San83}. Typically, these are found in centralized systems where the central acting authority is the main compromised agent. The DAO solves this by decentralizing the governance process by utilizing smart contracts running on open source blockchains.

@@

DAOSYS vision is to operate like a pure automated market maker (AMM) and be implemented in a manner that does not require external controls. In 2018, Uniswap became the first decentralized platform to successfully utilize an AMM \cite{Uni19}. However, like Uniswap and many AMMs, control of the capital in their respective liquidity pools is still centralized. DAOSYS intends to address this core issue via its new Autonomous Service Engine (ASE) technology \cite{Sys22}, hence allowing DAOs to be more autonomous and fully decentralized. The DAOSYS token is a smart DAO protocol that fully backed by an index of assets supported by its child DAOs. This technology will allow users to test, implement and realize countless decentralized finance (DeFi) usecase designs deployed in a secure manner through the ASE without having to continually redeploy new builds.

@@

\begin{itemize}
  \item Smart DAO protocol via hyper-diamond proxy
  \item Self-sovereign via trustless automatic integration
  \item Seamless fast deployment using secure templates
  \item Hyper-diamond standard
  \item Collateralized VE (vesting) indexing token
  \item Automated audits of child DAOs
  \item Fully backed (eg, DAI, SYS)
  \item Non-spectualtive asset
  \item No code or low code deploymments via user interface
  \item New emergent behavior and innovation for DeFi
\end{itemize}

@@

As the adage goes, \textit{if it’s not broke, don’t fix it}. The investment strategy implemented in a vault can be used across several instances of vault pools. This works well for new DAOs that wish to replicate the financial strategies of an existing DAO. Also, for when a new DAO would like to invest in other DAOs using the same strategy.

@@

These pools form the foundation of the DAO. Autonomous and permissionless liquidity pools that act as the agreed upon foundation for DAO treasury management. From there users may launch further liquidity pools that may accept the DAOs Treasury Token for deposit. These form the Roundtables for managing ventures within the DAO. The Roundtables compartmentalize management teams, Councilors, of the various ventures being executed under a DAO’s mission statement. A Roundtable typically does not have it’s own governance token, instead using a Council Token used to resolve disputes by executing buyout options.

From the Roundtables, any Councilor may use their contribution to the Roundtable to launch a bond offering for a Quest. Quests define the bounty award and terms for completing a task. The Councilor that issues the quest puts their share of the treasury in escrow to fund the Quest. The interest being earned from that underlying position is then split to fund the bounty, compound into that position, and to sell on the bond market. This ensures that Questors know the payment for work they deliver is secured. And protects the Councilor from failure to deliver; see Fig. \ref{fig:daosys_governance} for outline.

@@

Delegate Services replace the Facets defined in ERC-2535. Delegate Services define a strict storage allocation and access standard beyond the theory presented in ERC-2535. A Service is a smart-contract or library implemented following the Deterministically Dynamic Storage Allocation standard. A Service also reports the factory that deployed that contract and the salt used during deployment. This way the recalculation of the address from the factory init code hash and salt can be used to verify new Services as an implicit ACL.

This means that the deployment process for new Services deviates from industry standard. New Services are deployed as compiled bytecode passed to the Service Proxy Factory as the argument for the deployment function. The Service Proxy Factory then instantiates that bytecode as a new contract. ASE compliant Services must include the ASEServiceBootstrapper library to retrieve the address salt to initialize the Service. This should be done by delegating to the canonical external library deployment. ASE compliant external libraries may precalculate their address salt and store it as a constant. The standard Service initialization functions must still be implemented, but may hard code the values and return values since they can not store state.

All Services are required to implement ERC-165 including the Service extension that enumerates the functions. The Service extension to ERC-165 includes a per interface enumeration of the function selectors that define the interface ID. Additionally, there is an enumeration of all the function selectors across all interface IDs, and a ServiceDef struct that includes the information for initializing a Service Proxy to consume the Service.

\begin{figure}[h!]
\includegraphics[width=3in]{img/hyper_facet.png}
\caption{Hyper-facet} 
\label{fig:hyper_facet}
\end{figure}

@@

The main purpose of verified DAOs is to ensure that contributing DAOs are safe to transact with from a security standpoint as DAOSYS will know what contracts will be doing with storage and will be participating in the tokenomics model described in Section \ref{sec:tokenomics}. The public verified usecase will be the most common type of DAO on the network and are essentially clones of DAOSYS. With this comes the ability to create is own sub-network of child DAOs where it will receive the benefit of cascading royalties as illustrated in Fig. \ref{fig:clone_model}. The freedoms on launching a public verified DAO would akin to the GNU public licence in the sense that there would be certain freedoms that users would be permitted and not permitted to do with the source code.

@@

Included in this symbiotic relationship are several other benefits that child DAOs will have by joining this network over building its own standalone DAO. New DAOs benefit from significantly fast development time by selecting any one of the pre-vetted, secure DAOSYS templates. Included in this, DAOs can simulate the tokenomic behavior prior to launch using our Python simulator tailored to our system (as detailed in next Section) to build predictive models to determine 2-5 year estimated ROI calculations. DAOs that are part of our network will also benefit from the seamless integrations of working with other DAOs within our network. These integrations would be akin to the benefits nation states have when they join international trade agreements, where DAOSYS behaves as the overseeing regulatory body, and the child DAOs share attributes as participating nation states. These child DAOs also have the flexibility of cloning the DAOSYS factory and spawning its own sub-network within the DAOSYS ecosystem; see Fig. \ref{fig:clone_model}.

@@

The five steps of the tokenomics model described as a thought simulation Fig. \ref{fig:tokenomics_model} is as follows. In step A we assume the DAOSYS vault contains no assets, while the child DAO has 1000 SYS and 200 DAI. In step B we have a triggering event that stimulates a small deposit of 1 SYS and 0.2 DAI from the Child DAO vaults into the DAOSYS vaults. When this happens the DAOSYS vault will mint debt tokens of these newly aquired assets with a 1:1 backing. In exchange for these assets, the child DAO will receive newly minted index tokens that represent a 1:1 backing by DAOSYS. Next in step C, DAOSYS will send both these debt and collateral tokens through a DeFi investment engine. Over time, the DAOSYS vault will collect interest from these newly acquired collateral and debt assets, as seen in step D. The child child can either keep these collateral in DAOSYS to continue to collect interest or recall the collateral. Hence, in the final stage E of this process, the child DAO recalls the original collateral and all its earned interest, while DAOSYS keeps the debt interest. Once the child DAOs collateral and interest is withdrawn, both dept and index tokens are burned. When comparing the final step to the initial step, we see that both DAOSYS and the child DAO see a net positive gain in liquidity. The child DAO will collect interest from its own collateral, while DAOSYS will collect interest from the debt created from that collateral.

@@

\subsection{DeFi Python Simulator}

@@

With this tool, DAOSYS designers can utilize the plug and play components of our simulator to build tokenomics mockups for business planning purposes so that teams can come together and get collective consensus alongside potential users and investors. Not only is this tool applicable to DAOSYS, it can be used as a general purpose tool to simulate DEX activity for anyone wishing to setup their own liquidity pool (LP) and wish to stress test their ideas prior to development. This can be used as a powerful design tool to explore the limitations of an DeFi project idea prior to committing valuable resources on development costs (ie, Devs and Project Managers). Table \ref{table:simulator_components} highlights the main components of the simulator, so that potential users of the system can get a higher level understanding of how the simulator package functions.

@@

The purpose of this tool is primarily for the design aspect of DAOSYS, and is still in its early stages of development. The next stages involve feeding the output of various mathematical models into the simulator framework and to use this tool to simulate other DeFi usecases. This is so that we can test a roster of edge cases to build more robust systems. The final goal is to bring this system to a level of maturity so that it can be utilized in parallel with the contracts in real time. Hence, opening up DeFi to a more scientific way of design, test, and implementation.

@@

Currently, there are approximately 2,500 Masternodes running on the Syscoin network. In \cite{Moo22A}, we ran a case study with a 5-year projection analysis on an additional 400 Masternodes, while at the same time factoring in network growth. We applied all these components into our model to estimate daily supply growth of the network, along with its respective confidence intervals; see Appendix \ref{sec:masternode_tokenomics} for details. With this tokenomics model, we estimated the expected share a typical node contributes to the network on a daily basis. Finally, with expected share, we estimated the 5-year output of 400 new Masternodes; see Table \ref{table:mn_returns} for details.

\begin{figure}[h!]
\includegraphics[width=3in]{img/supply_tot_reward_output.png}
\caption{Predicted five-year returns from 400 new Syscoin masternodes starting Jan 2023, which include both net positive yields from both Masternode and DAOSYS; (TOP) daily returns; and (BOTTOM) cumulative returns. Overall, we are predicting an overall return of 14.7M SYS which represents a 5-year return of 36.8\% from the original investment of 40M SYS. Without DAOSYS, we would only realize an overall return of 31.2\%; for methodology see Appendix B.} 
\label{fig:reward_output}
\end{figure}

@@

The Syscoin Foundation will allocate \$20M SYS into SYS Labs. At approx. \$27M USD peak valuation, SYS Labs will execute the master node yield strategy using its rewards. This will enable liquidity events which investors of SYS Labs can execute on through token warrants in exchange for equity. Masternode ROI will be used to deposit into DAOSYS which will be used to fund ecosystem initiatives as well as pay out token warrants to SYS Labs investors looking to exit. Analysis on Masternode ROI based on price modelling through to year 2028; see \cite{DAOSim22} for Jupyter notebook. Analysis on DAOSYS ROI based on price modelling through to year 2025 (not including value created through lending to builders to build ecosystem objectives); see \cite{DAOSim22}.

@@

To put into perspective, under John Boogle’s direction, Vanguard is credited with the creation of the first index fund which was made available to the individual investor \cite{Bog17}. This index fund was created in 1957, and was passively tied to the performance of the S\& P 500. Boogle is known as the founder of The Vanguard Group, which as of today (ie, Sept 2022), manages \$7 trillion in assets. When investing long-term, Boogle argues the most efficient way to invest, is to simply buy the market itself, and that over time when looking at funds as a whole, they as a collective always revert to the mean. He also argues that over time, actively managed funds underperform the market, no matter what the current performance is.

@@

\begin{itemize}
  \item ETH and BTC have been the top two projects by market cap for the past 5 years
  \item ETH is a good proxy for the altcoin market which perform better in bull markets, while BTC is a good proxy for crypto gold which perform better in bear markets
  \item By referencing Fig. 2, we can see the combined market cap share of the crypto space of both of these two projects has fluctuated between 60-90\%
  \item Market cap share between ETH and BTC is negatively correlated against each other (p-val $\sim$ 0)
  \item ETH encapsulates large portions of other sectors (DeFi, NFT, etc) of the crypto space
\end{itemize}

@@

It is surprising that with all the developments that have happened in crypto, and given the success that ETFs have had in traditional finance we have not yet seen adoption of this idea into crypto yet. However, DAOSYS with its smart DAO features will allow for the secure and seamless deployment of these new class of cryptos.

@@

We are expecting to launch DAOSYS in the early part of 2023 with crypto's first Masternode Yield Farm as its first functioning child DAO; see Fig. \ref{fig:daosys_launch}. Hence other projects running Masternodes will be incentivised to use our template and join the ecosystem to earn additional yield following the business case outlined in Section \ref{sec:yield_farming}.

@@

A proxy contract is the the immutable part a user interacts with which holds data. It contains a fallback function which will catch any function call and use \texttt{delegatecall} to forward it to a second logic contract. As a reminder, \texttt{delegatecall} will execute a function defined in the called contract (logic), but within the context of the calling contract (proxy). Thus, we have our logic defined separately from our data. This allows users to change the logic contract without changing the immutable underlying data.

@@

The Masternode Yield Farming tokenomics model has two main components: (a) Masternode rewards; and (b) DAOSYS rewards. To aquire Masternode rewards, users stake liquidity to purchase a Masternode, thus used to generate $Coins_{New}$ in accordance to the specifications described in \cite{Sig21b}, which are as follows:

\begin{itemize}
\item \textbf{Block time:} 150 seconds
\item \textbf{Halving interval:} 210240 (1 year)
\item \textbf{Base Rewards:}  96.25 SYS per block deflated 5 percent every 210240 blocks
\item \textbf{NEVM Rewards:}  10.55 SYS per block (not deflated). EIP1559 model
\item \textbf{Governance Proposals:}  10 percent of Base Rewards paid out every 17520 blocks (1 month)
\item \textbf{Miner/Masternode Subsidy:}  90 percent of Base Rewards. 25 percent of this value goes to miner, 75 percent of this value goes to masternode
\item \textbf{Masternode Minimum Subsidy:} 5.275 SYS (can not go below this amount even accounting for deflation)
\item \textbf{Masternode collateral requirement:} 100,000 SYS
\item \textbf{Masternode seniority}: 35 percent increase after 210240 blocks (1 year), 100 percent increase after 525600 blocks (2.5 years)
\end{itemize}
Using the rule set described above, we determine Masternode rewards via the following: 
\begin{equation*}
MN_{Rewards} = (Blocks_{Num}) (Coins_{New}) \left(\frac{Nodes_{Num}}{Supply_{Cur}}\right),
\end{equation*}
where current supply is calculated via the following:
\begin{equation*}
Supply_{Cur} = Supply_{Prev} + Coins_{New} - Fee_{TXBurn},
\end{equation*}
and $Fee_{TXBurn}$ is calculated in accordance to Section \ref{appendix:tx_fee_burn}. Finally, total rewards were determined via the following: 
\begin{equation*}
Total_{Rewards} = MN_{Rewards} + DAOSYS_{Rewards}. 
\end{equation*}
To estimate $DAOSYS_{Rewards}$, we used our DeFi python simulator; for tutorials and example templates one can reference \cite{Moo22B}. To estimate returns in USD, we applied the Monte Carlo procedure to estimate future point predictions for the USD value of Syscoin, as per Section \ref{appendix:monte_carlo}.

@@

\subsection{Point Price Predictions: Monte Carlo}
\label{appendix:monte_carlo}
To generate point predictions for the price of Syscoin, we made some assumptions. Price was given the freedom to fluctuate between \$0.25 to \$25 USD / SYS over the 5-year projection interval (ie, 2023-2028) while maintaining an overall upward logarithmic growth, which is a price behavior characteristic that can be attributed to most successful crypto projects. To do this we generated a set of Monte Carlo point predictions, $\mathbf{\hat{p}}_{t}$, using the following:

\begin{equation}
\label{eqn:trend}
	\mathbf{\hat{p}}_{t} = c + \mathbf{\tilde{z}}_{t}e^{k z_{t}},
\end{equation}
where random drift term $\mathbf{\tilde{z}}_{t}$ is normalized between the interval [$a_{lwr}$,$a_{upr}$] as given by:
\begin{equation}
\label{eqn:min_max}
	\mathbf{\tilde{z}}_{t}= \frac{\mathbf{z}_{t} - min(\mathbf{z}_{t})}{max(\mathbf{z}_{t}) - min(\mathbf{z}_{t})},
\end{equation}
and $\mathbf{z}_{t}$ is an ARIMA(1,1,1) process, given by:
\begin{equation}
\label{eqn:drift}
	\mathbf{z}_{t} = \gamma + \mathbf{z}_{t-1} + \phi_{1} \mathbf{z}_{t-1} - \phi_{1} \mathbf{z}_{t-2} +  \theta_{1} \mathbf{e}_{r-1} + \mathbf{e}_{t},
\end{equation}
where $\phi_{1}$ is the AR(1) coefficient, $\theta_{1}$ is the MA(1) coeffcient, and $\mathbf{e}_{t} \sim N(0, \sigma^2)$. Once these sets were generated, we estimated the 5$^{th}$ and 95$^{th}$ percentiles to attain the 90\% prediction interval. Refer to \cite{Moo22A} for a table of these point predictions, along with its corresponding confidence interval.

>>>>

\documentclass[journal,twocolumn,12pt]{ieeesyscoin}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{lipsum}
\usepackage{makecell}
\usepackage[switch]{lineno}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\history{}

@@

\begin{abstract}
Despite popular perception, treasuries of Decentralized Autonomous Organizations (DAOs) tend to be centrally controlled and do not reflect the true ethos of cryptocurrency (i.e., \textit{not your keys, not your coins}). DAOSYS solves this problem with its new Autonomous Service Engine (ASE) technology by deploying a reference platform for self-sovereign capital coordination. Through the ASE, the DAOSYS token will serve as a protocol layer creating a fully backed non-speculative asset allowing for quick seamless deployment of child DAOs in a secure manner. This is made possible by innovating on the multi-faceted proxy standard defined in EIP-2535. The ASE will serve as the cornerstone of all SYS Labs decentralized finance (DeFi) products, as supported by the Syscoin Platform.
\end{abstract}

@@

The objective of a decentralized autonomous organization (DAO) is to solve the principal-agent dilemma. This dilemma is a result of misaligned incentives where agents acting in a system are incentivized towards their own benefit over the benefit of a principle or other agents acting within the system \cite{San83}. Typically, these are found in centralized systems where the central acting authority is the main compromised agent. The DAO solves this by decentralizing the governance process through the utilizing of smart contracts running on open source blockchains.

@@

DAOSYS vision is to operate like a pure automated market maker (AMM) and be implemented in a manner that does not require external controls. In 2018, Uniswap became the first decentralized platform to successfully utilize an AMM \cite{Uni19}. However, like Uniswap and many AMMs, control of the capital in their respective liquidity pools is still centralized. DAOSYS intends to address this core issue via its new Autonomous Service Engine (ASE) technology \cite{Sys22}, hence allowing DAOs to be more autonomous and fully decentralized. The DAOSYS token is a smart DAO protocol is that fully backed by an index of assets supported by its child DAOs. This technology will allow users to test, implement and realize countless decentralized finance (DeFi) usecase designs deployed in a secure manner through the ASE without having to continually redeploy new builds.

@@

\begin{itemize}
  \item Smart DAO protocol via hyper-diamond proxy
  \item Self-sovereign via trustless automatic integration
  \item Seamless fast deployment using secure templates
  \item Hyper-diamond standard
  \item Collateralized VE (vesting) indexing token
  \item Automated audits of child DAOs
  \item Fully backed (eg, DAI, SYS)
  \item Non-speculative asset
  \item No code or low code deployments via user interface
  \item New emergent behavior and innovation for DeFi
\end{itemize}

@@

As the adage goes, \textit{if it’s not broke, don’t fix it}. The investment strategy implemented in a vault can be used across several instances of vault pools. This works well for new DAOs that wish to replicate the financial strategies of an existing DAO. Also, this also works for when a new DAO would like to invest in other DAOs using the same strategy.

@@

These pools form the foundation of the DAO. Autonomous and permissionless liquidity pools that act as the agreed upon foundation for DAO treasury management. From there users may launch further liquidity pools that may accept the DAO's Treasury Token for deposit. These form the Roundtables for managing ventures within the DAO. The Roundtables compartmentalize management teams, Councillors, of the various ventures being executed under a DAO’s mission statement. A Roundtable typically does not have it’s own governance token, instead using a Council Token to resolve disputes by executing buyout options.

From the Roundtables, any Councillor may use their contribution to the Roundtable to launch a bond offering for a Quest. Quests define the bounty award and terms for completing a task. The Councillor that issues the Quest puts their share of the treasury in escrow to fund it. The interest being earned from that underlying position is then split to fund the bounty, compound into that position, and to sell on the bond market. This ensures that Questors know the payment for work they deliver is secured. And protects the Councilor from failure to deliver; see Fig. \ref{fig:daosys_governance} for outline.

@@

Delegate Services replace the Facets defined in ERC-2535; see Fig. \ref{fig:hyper_facet}. Delegate Services define a strict storage allocation and access standard beyond the theory presented in ERC-2535. A Service is a smart-contract or library implemented following the Deterministically Dynamic Storage Allocation standard. A Service also reports the factory that deployed that contract and the salt used during deployment. This way the recalculation of the address from the factory init code hash and salt can be used to verify new Services as an implicit ACL.

This means that the deployment process for new Services deviates from industry standard. New Services are deployed as compiled bytecode passed to the Service Proxy Factory as the argument for the deployment function. The Service Proxy Factory then instantiates that bytecode as a new contract. ASE compliant Services must include the \texttt{ASEServiceBootstrapper} library to retrieve the address salt to initialize the Service. This should be done by delegating to the canonical external library deployment. ASE compliant external libraries may precalculate their address salt and store it as a constant. The standard Service initialization functions must still be implemented, but may hard code the values and return values since they can not store state.

All Services are required to implement ERC-165 including the Service extension that enumerates the functions. The Service extension to ERC-165 includes a per interface enumeration of the function selectors that define the interface ID. Additionally, there is an enumeration of all the function selectors across all interface IDs, and a \textit{ServiceDef} struct that includes the information for initializing a Service Proxy to consume the Service.

\begin{figure}[h!]
\includegraphics[width=3in]{img/hyper_facet.png}
\caption{Hyper-facet consisting of delegate Services that replace facets defined in ERC-2535} 
\label{fig:hyper_facet}
\end{figure}

@@

The main purpose of verified DAOs is to ensure that contributing DAOs are safe to transact with from a security standpoint, as DAOSYS will know what contracts will be doing with storage and will be participating in the tokenomics model described in Section \ref{sec:tokenomics}. The public verified usecase will be the most common type of DAO on the network and are essentially clones of DAOSYS. With this comes the ability to create is own sub-network of child DAOs where it will receive the benefit of cascading royalties as illustrated in Fig. \ref{fig:clone_model}. The freedoms on launching a public verified DAO would akin to the GNU public licence in the sense that there would be certain freedoms that users would be permitted and not permitted to do with the source code.

@@

Included in this symbiotic relationship are several other benefits that child DAOs will have by joining this network over building its own standalone DAO. New DAOs benefit from significantly fast development time by selecting any one of the pre-vetted, secure DAOSYS templates. Included in this, DAOs can simulate the tokenomic behavior prior to launch using our Python simulator tailored to our system (as detailed in Section \ref{sec:python_simulator}) to build predictive models to determine future estimated ROI calculations. DAOs that are part of our network will also benefit from the seamless integrations of working with other participating DAOs. These integrations would be akin to the benefits nation states have when they join international trade agreements, where DAOSYS behaves as the overseeing regulatory body, and the child DAOs share attributes as participating nation states. These child DAOs also have the flexibility of cloning the DAOSYS factory and spawning its own sub-network within the DAOSYS ecosystem; see Fig. \ref{fig:clone_model}.

@@

The five steps of the tokenomics model described in Fig. \ref{fig:tokenomics_model} are as follows. In step A we initially assume DAOSYS vaults contains no assets, while the child DAO vaults have 1000 SYS and 200 DAI. In step B we have a triggering event that stimulates a small deposit of 1 SYS and 0.2 DAI from the Child DAO vaults into the DAOSYS vaults. When this happens the DAOSYS vault will mint debt tokens of these newly acquired assets with a 1:1 backing. In exchange for these assets, the child DAO will receive newly minted index tokens that represent a 1:1 backing by DAOSYS. Next in step C, DAOSYS will send both these debt and collateral tokens through a DeFi investment engine. Over time, the DAOSYS vault will collect interest from these newly acquired collateral and debt assets, as seen in step D. The child DAO can either keep these collateral in DAOSYS and continue to collect interest or recall the collateral. Hence, finally in step E of this process, the child DAO recalls the original collateral and all its earned interest, while DAOSYS keeps the debt interest. Once the child DAOs collateral and interest is withdrawn, both dept and index tokens are burned. When comparing the final step to the initial step, we see that both DAOSYS and the child DAO see a net positive gain in liquidity. The child DAO will collect interest from its own collateral, while DAOSYS will collect interest from the debt created from that collateral.

@@

\subsection{DeFi Python Simulator}
\label{sec:python_simulator}

@@

With this tool, DAOSYS designers can utilize the plug and play components of our simulator to build tokenomics mockups for business planning purposes so that teams can come together and get collective consensus alongside potential users and investors. Not only is this tool applicable to DAOSYS, it can be used as a general purpose tool to simulate DEX activity for anyone wishing to setup their own liquidity pool (LP) and wish to stress test their ideas prior to development. This can be used as a powerful design tool to explore the limitations of an DeFi project idea prior to committing valuable resources on development costs (ie, Devs and Project Managers). Table \ref{table:simulator_components} highlights the main components of the simulator, so that potential users of the system can get a higher level understanding of the DeFi simulator package.

@@

The purpose of this tool is primarily for the design aspect of DAOSYS, and is still in its early stages of development. The next stages involve feeding the output of various mathematical models into the simulator framework and to use this tool to simulate other DeFi usecases. This is so that we can test a roster of edge cases to build more robust systems. The final goal is to bring this system to a level of maturity so that it can be utilized in parallel with the contracts in real time. Hence, exposing DeFi to a scientific way of design, testing, and implementation.

@@

Currently, there are approximately 2,500 Masternodes running on the Syscoin network. In \cite{Moo22A}, we ran a case study with a five-year projection analysis on an additional 400 Masternodes, while at the same time factoring in network growth. We applied all these components into our model to estimate daily supply growth of the network, along with its respective confidence intervals; see Appendix \ref{sec:masternode_tokenomics} for details. Overall, we are predicting an overall return of 14.7M SYS which represents a five-year return of 36.8\% from the original investment of 40M SYS; see Fig. \ref{fig:reward_output}. Without DAOSYS, we would only realize an overall return of 31.2\%; for methodology see Appendix B. Keep in mind that the principle investment of 100K SYS is not subject to any risk, and the estimated DAOSYS returns is working from Masternode returns as its principle. With this tokenomics model, we estimated the expected share a typical node contributes to the network on a daily basis. Finally, with expected share, we estimated the five-year output of 400 new Masternodes; see Table \ref{table:mn_returns} for details.

\begin{figure}[h!]
\includegraphics[width=3in]{img/supply_tot_reward_output.png}
\caption{Predicted five-year returns from 400 new Syscoin masternodes starting Jan 2023, which include both net positive yields from both Masternode and DAOSYS; (TOP) daily returns; and (BOTTOM) cumulative returns.} 
\label{fig:reward_output}
\end{figure}

@@

The Syscoin Foundation will allocate \$20M SYS into SYS Labs. At an estimated \$27M USD peak valuation for 2023, SYS Labs will execute the master node yield strategy using its rewards. This will enable liquidity events which investors of SYS Labs can execute on through token warrants in exchange for equity. Masternode ROI will be used to deposit into DAOSYS which will be used to fund ecosystem initiatives as well as pay out token warrants to SYS Labs investors looking to exit. Analysis on Masternode ROI based on price modelling through to year 2028; see \cite{DAOSim22} for Jupyter notebook. Analysis on DAOSYS ROI based on price modelling through to year 2025 (not including value created through lending to builders to build ecosystem objectives); see \cite{DAOSim22}.

@@

To put into perspective, under John Boogle’s direction, Vanguard is credited with the creation of the first index fund which was made available to the individual investor \cite{Bog17}. This index fund was created in 1957, and was passively tied to the performance of the S\&P 500. Boogle is known as the founder of The Vanguard Group, which as of today (ie, Sept 2022), manages \$7 trillion in assets. When investing long-term, Boogle argues the most efficient way to invest, is to simply buy the market itself, and that over time when looking at funds as a whole, they as a collective always revert to the mean. He also argues that over time, actively managed funds underperform the market, no matter what the current performance is.

@@

\begin{itemize}
  \item ETH and BTC have been the top two projects by market cap for the past 5 years
  \item ETH is a good proxy for the altcoin market which perform better in bull markets, while BTC is a good proxy for crypto gold which perform better in bear markets
  \item The combined market cap share of the crypto space of both of these two projects has fluctuated between 60-90\%
  \item Market cap share between ETH and BTC is negatively correlated against each other (p-val $\sim$ 0)
  \item ETH encapsulates large portions of other sectors (DeFi, NFT, etc) of the crypto space
\end{itemize}

@@

It is surprising that with all the developments that have happened in crypto, and given the success that ETFs have had in traditional finance, we have not yet seen adoption of this idea into crypto yet. However, DAOSYS with its smart DAO features will allow for the secure and seamless deployment of these new class of cryptos.

@@

We are expecting to launch DAOSYS in the early part of 2023 with crypto's first Masternode Yield Farm as its first functioning child DAO; see Fig. \ref{fig:daosys_launch}. Hence other projects running Masternodes will be incentivized to use our template and join the ecosystem to earn additional yield following the business case outlined in Section \ref{sec:yield_farming}.

@@

A proxy contract is the the immutable part a user interacts with which holds data. It contains a fallback function which will catch any function call and use \texttt{delegatecall} to forward it to a second logic contract. A \texttt{delegatecall} will execute a function defined in the called contract (logic), but within the context of the calling contract (proxy). Thus, we have our logic defined separately from our data. This allows users to change the logic contract without changing the immutable underlying data.

@@

The Masternode Yield Farming tokenomics model has two main components: (a) Masternode rewards; and (b) DAOSYS rewards. To acquire Masternode rewards, users stake liquidity to purchase a Masternode, thus used to generate $Coins_{New}$ in accordance to the specifications described in \cite{Sig21b}, which are as follows:

\begin{itemize}
\item \textbf{Block time:} 150 seconds
\item \textbf{Halving interval:} 210240 (1 year)
\item \textbf{Base Rewards:}  96.25 SYS per block deflated 5 percent every 210240 blocks
\item \textbf{NEVM Rewards:}  10.55 SYS per block (not deflated). EIP1559 model
\item \textbf{Governance Proposals:}  10 percent of Base Rewards paid out every 17520 blocks (1 month)
\item \textbf{Miner/Masternode Subsidy:}  90 percent of Base Rewards. 25 percent of this value goes to miner, 75 percent of this value goes to Masternode
\item \textbf{Masternode Minimum Subsidy:} 5.275 SYS (can not go below this amount even accounting for deflation)
\item \textbf{Masternode collateral requirement:} 100,000 SYS
\item \textbf{Masternode seniority}: 35 percent increase after 210240 blocks (1 year), 100 percent increase after 525600 blocks (2.5 years)
\end{itemize}
Using the rule set described above, we determine Masternode rewards via the following: 
\begin{equation*}
MN_{Rewards} = (Blocks_{Num}) (Coins_{New}) \left(\frac{Nodes_{Num}}{Supply_{Cur}}\right),
\end{equation*}
where current supply is calculated via the following:
\begin{equation*}
Supply_{Cur} = Supply_{Prev} + Coins_{New} - Fee_{TXBurn},
\end{equation*}
and $Fee_{TXBurn}$ is calculated in accordance to Section \ref{appendix:tx_fee_burn}. Finally, total rewards were determined via the following: 
\begin{equation*}
Total_{Rewards} = MN_{Rewards} + DAOSYS_{Rewards}. 
\end{equation*}
To estimate $DAOSYS_{Rewards}$, we used our DeFi python simulator; for tutorials and example templates one can reference \cite{Moo22B}. To estimate returns in USD, we applied the Monte Carlo procedure to estimate future point predictions for the USD value of Syscoin, as per Section \ref{appendix:monte_carlo}.

@@

\subsection{Price Point Predictions: Monte Carlo}
\label{appendix:monte_carlo}
To generate point predictions for the price of Syscoin, we made some assumptions. Price was given the freedom to fluctuate between \$0.25 to \$25 USD / SYS over the five-year projection interval (ie, 2023-2028) while maintaining an overall upward logarithmic growth, which is a price behavior characteristic that can be attributed to most successful crypto projects. To do this we generated a set of Monte Carlo point predictions, $\mathbf{\hat{p}}_{t}$, using the following:

\begin{equation}
\label{eqn:trend}
	\mathbf{\hat{p}}_{t} = c + \mathbf{\tilde{z}}_{t}e^{k z_{t}},
\end{equation}
where random drift term $\mathbf{\tilde{z}}_{t}$ is normalized between the interval [$a_{lwr}$,$a_{upr}$] as given by:
\begin{equation}
\label{eqn:min_max}
	\mathbf{\tilde{z}}_{t}= \frac{\mathbf{z}_{t} - min(\mathbf{z}_{t})}{max(\mathbf{z}_{t}) - min(\mathbf{z}_{t})},
\end{equation}
and $\mathbf{z}_{t}$ is an ARIMA(1,1,1) process, given by:
\begin{equation}
\label{eqn:drift}
	\mathbf{z}_{t} = \gamma + \mathbf{z}_{t-1} + \phi_{1} \mathbf{z}_{t-1} - \phi_{1} \mathbf{z}_{t-2} +  \theta_{1} \mathbf{e}_{r-1} + \mathbf{e}_{t},
\end{equation}
where $\phi_{1}$ is the AR(1) coefficient, $\theta_{1}$ is the MA(1) coefficient, and $\mathbf{e}_{t} \sim N(0, \sigma^2)$. Once these sets were generated, we estimated the 5$^{th}$ and 95$^{th}$ percentiles to attain the 90\% prediction interval. For a table of these point predictions along with its corresponding confidence interval, see \cite{Moo22A}.
